\section{Introduction}
\subsection{Problem Description}
From the group project assignment:
\vspace{0.4cm}

\textit{In a \textbf{slotted random-access network}, \textbf{N couples transmitter-receiver} share the same communication
medium, which consists of \textbf{C separate channels}. Multiple attempts to use the same channel in the
same slot by different transmissions will lead to collision, hence no receiver listening on that
channel will be able to decode the message.
Assume that each of the N transmitters generate packets according to an \textbf{exponential inter-arrival
distribution}, and picks its channel at random on every new transmission. Before sending a packet, it
keeps extracting a value from a \textbf{Bernoullian RV with success probability p} on every slot, until it
achieves success. Then it transmits the packet and starts over. If a collision occurs, then the
transmitter backs off for a random number of slots (see later), and then starts over the whole
Bernoullian experiment.
The number of back-off slots is extracted as $U(1, 2^{x+1})$, where x is the number of collisions
experienced by the packet being transmitted.}
\subsection{Objectives}
The aim of the project report is the \textit{Assessment of the Effectiveness of the Slotted Random-Access Network Protocol} described in the latter paragraph.
\subsection{Performance Indexes}
In order to define a metric of performance of the objective, the following Performance Indexes are defined:
\begin{itemize}
	\item \textbf{Throughput}: let $Tp$ be the Throughput to be measured, $N_{p}$ the number of packets successfully sent to the corresponding receiver, $N_{t}$ the number of time-slot considered in the count of $N_{p}$, $T_{slot}$ the period (in seconds) of a time slot, the Throughput(per slot) can be measured as:
	\begin{align*}
	Tp(slot) = \frac{N_{p}}{N_{t}} \quad [packets/slot]
	\end{align*}
	During all the documentation the latter will be used because more meaningful w.r.t. the scenario that will be defined.
	We can also convert this performance metric in a more standard form, dealing with packets per second:
	\begin{align*}
	Tp = \dfrac{Tp(slot)}{T_{slot}} \quad [packets/s]
	\end{align*}
	
	
	\item \textbf{Response Time}: defined as the time that occurs from the first appearance of one packet at the Transmitter up to the reception of the packet at the Receiver.
	
	%\item \textbf{Mean Number of Packets in the queues}: due to the fact that the this metric is time dependent, will be computed as:
	%\begin{align*}
	%E[N] = \frac{\sum_{i = 0}^{N}N_{i}*(t_{i+1} - t_{i})}{t_{N} - t_{0}} \quad 
	%\end{align*}
	%Where $N_{i}$ are the number of packets in the buffer on the interval $[t_{i}, t_{i+1})$.
\end{itemize}